---
title: "Project_"
output: html_document
---
Read the file in R (the original file is save as a .dta -used in Stata-)
```{r setup, include=FALSE}
replication_ajr= read.dta("C:/Users/user/Documents/lorenzo-verstraeten/propulsion_lorenzo/Module_2_Statistics/maketable1.dta", convert.factors=FALSE)
#be sure to have the "foreign" package and to point at the right directory

View(replication_ajr)
```

Running OLS and Plot

```{r}
st_lm=lm(replication_ajr$logpgp95 ~ replication_ajr$avexpr, data = STATA2)
summary(st_lm)

plot(replication_ajr$avexpr, replication_ajr$logpgp95, main="GDP vs Institution",
   xlab="Average protection against expropriation", ylab="log(per_capita_GDP_1995)",xlim=c(3.5, max(replication_ajr$avexpr, na.rm=T)),    ylim=c(6, max(replication_ajr$logpgp95, na.rm=T)))

abline(st_lm)

text(replication_ajr$avexpr, replication_ajr$logpgp95, labels=replication_ajr$shortnam, cex=0.6)
```
Test the first stage setller mortality vs institutions measure

```{r}
lm_settle=lm(replication_ajr$avexpr ~ replication_ajr$logem4, data = replication_ajr)
summary(lm_settle)


plot(replication_ajr$logem4, replication_ajr$avexpr, main="Institution vs settler moratlity", 
     xlab="log(mortality)", ylab="Average protection against expropriation",
     xlim=c(1, max(replication_ajr$logem4, na.rm=T)), ylim=c(3, max(replication_ajr$avexpr, na.rm=T)))

abline(lm_settle)

text(replication_ajr$logem4, replication_ajr$avexpr, labels=replication_ajr$shortnam, cex=0.6)
```
Running the IV regression. Note the change in the estimate. This is the causal effect of institution on GDP

```{r}
iv_=ivreg(replication_ajr$logpgp95 ~ replication_ajr$avexpr | replication_ajr$logem4 , data = replication_ajr)
summary(iv_)
```


Playing with bootstrap and residuals (not part of the original paper)

bootstrap the mean for our dependent variable log(GDP in 1995)

```{r , echo=FALSE}


calc_mean = function(data, index){
  mean_x <- mean(replication_ajr$logpgp95[index], na.rm=TRUE) 
  return(mean_x)
}

bootobject = boot(replication_ajr$logpgp95, calc_mean, R=10000) #be sure to have the boot pacakage
bootobject
boot.ci(bootobject, type="bca") #compute mean confidence intervals

```


residuals of the first OLS

```{r}
plot(st_lm)
```

We bootstrap the coefficient of the first OLS regression

```{r}
vec=numeric(1000)
for (i in 1:1000){
    #we generate a lot of estimate for beta from random sub-sample and we get a vector with all these.
    index_beta=sample.int(length(replication_ajr$shortnam), 30)
    vec[i]=(summary(lm(replication_ajr$logpgp95[index_beta] ~     replication_ajr$avexpr[index_beta]))$coefficient[2])
}


hist(vec)
mean(vec) #mean of bootstraps
quantile(vec,0.025) #confidence interval
quantile(vec,0.975)
```


